Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-25 WRITEUP/ms.tex
updated SED section with SFR and comparison to C13 sameple, but LIR and FIR/IR fraction, etc

\subsection{SED modeling} \label{sec:SED}
We fit dust SED models to the
24\micron$-$2.2\,mm photometry in \Fig{SED}, where we also
include the IRAS 60$\micron$ and 100$\micron$ upper limits
to constrain the dust peak.
The fit is performed with the code
\ncode{mbb\_emcee} \citep[\eg][]{Dowell14a}, which samples the posterior
using an MCMC approach and uses instrumental
response curves to perform color correction on-the-fly.
The SED model consists of a modified-blackbody
function with a power-law attached to the
Wien side to account for an excess in the MIR owing to warm,
small dust emission.
% Previous studies find that in the absence of mid-IR data, a powerlaw slope
% of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, % for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
%
%We add $\sim$15\% calibration uncertainties in quadrature to obtain the total
%uncertainties for the PdBI continuum in our fitting procedure.
The model is thus described by five free parameters: the rest-frame characteristic dust
temperature (T$_{d}$), the emissivity index ($\beta$), the power-law index
($\alpha$), the flux normalization at 500$\micron$ ($f_{\rm norm}$), and
the observed-frame wavelength at which the emission
becomes optically thick ($\lambda_{0}$). We impose
an upper limit of 100\,K on $T_d$, a Gaussian prior centered around
$\mu$\,=\,1.9 with $\sigma$\,=\,0.3 on $\beta$, and an upper limit of
1000$\micron$ on $\lambda_0$.
We check for chain convergence by requiring the autocorrelation
length of each parameter to be less than the number of steps
taken for the burn-in phase (which are then discarded).
Here we report the modes %in log file
% summary statistics (global mode (where min. chi),
% marginal mode (in log file), posterior median (instead of posterior means;
% need to compute)
and the 1$\sigma$ confidence intervals in the marginal PDFs
as the best-fit parameters, as listed in \Tab{SED}.

@@

In the first model, we include the 24$\micron$ data
to constrain the power-law index. Based on the
best-fit of this model, we find a
\fir luminosity (rest-frame 42.5-122.5\,$\micron$) of
3.81\petm{2.04}{-1.92}\E{12}\,\Lsun and a
dust mass of 22\petm{5}{-18}\E{8}\,\Msun.
For the mass absorption coefficient, we adopt
$\kappa$\,=\,2.64\,m$^2$kg\pmOne at 125.0$\micron$
(rest frame; \citealt{Dunne03a}).
The dust mass uncertainty does not
include those in the absorption coefficient.
These values are not corrected for lensing.

A fit including the MIR 24$\micron$ photometry
is likely an upper limit on the \fir luminosity arising from starburst.
% since the fit include contribution from the AGN (through power-law to MIR)
If we instead fit for a model excluding the 24$\micron$ constraint,
two major consequences are immediately apparent.
First, the power-law index is poorly-constrained (see \Tab{SED}).
Second, the steep power-law implies a small contribution
from the power-law regime
to the total IR luminosity as compared to the graybody.
Thus, the \fir luminosity in
this model should, in principle, corresponds to a
lower limit on the cold dust emission.
Using the best-fit parameters
for this model, we find a  \LFIR of 4.72\petm{2.54}{-2.26}\E{12}\,\Lsun and a $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun.
Again, the inferred quantities are uncorrected for lensing.
%The best-fit SEDs are shown in \Fig{SED} and the
% resulting parameters are listed in \Tab{SED}.

The dust temperature from both models is consistent with that
of ULIRGs at 0.6\,$<$\,$z$\,$<$\,1.0 (54\,$\pm$\,5\,K, \citealt{Combes13a}).
We note the \fir luminosities from both models are comparable, which is
not surprising given the lack of constraints in the MIR. In fact, the
\fir luminosity from the latter fit is slightly higher than the former, but
consistent within their uncertainties.
For the subsequent analysis, we adopt the physical quantities
from the former model. The choice of which fit does not affect
the derived star formation rate (SFR) given the similar \LFIR.
Yet, the dust mass is higher in the former model (but consistent within the
uncertainties), and thus the gas-to-dust ratio in \Sec{properties} 
should be considered as an estimate.

@@

We correct for lensing using the median magnification factor 
derived from the CO lens models. Assuming a Salpeter initial 
mass function, we find the SFR of blah using a standard SK law.

\subsection{Gas properties} \label{sec:properties}
In this section, we derive the gas properties of RXJ1131 based on \bco,
and compare the derived quantities against those reported by
\citet[hereafter C13]{Combes13a}, which is the largest sample of
ULIRGs at intermediate redshift (0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements,
to place RXJ1131 in context of existing studies. Their results are
based on \bco and \rot{4}{3} line observations on the IRAM 30-m dish.

@@

Without direct \rot{1}{0} measurements,
we derive \rot{1}{0} intensity
using a brightness temperature ratio of $r_{\rm 32}$\,=\,1, which was chosen
solely to facilitate a comparison with the C13 sample. For the same reason, we
adopt a luminosity-to-mass conversion factor of
\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne. This yields
\Lp\,=\,(3.47\,$\pm$\,1.58)\E{10}\,\Lsun and a gas mass
of (2.8$\pm$1.3)\,\E{10} \Msun. This is likely
an overestimation due to a contribution from the companion, but is
nevertheless consistent with the C13 sample ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) within the
uncertainties.

% gas-to-dyn ratio
Using the dynamical mass of BLAH (see \Sec{dynamics}), we find
a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
% gas to dust ratio:
Based on the dust mass derived from SED fitting, we find a gas-to-dust ratio of
$f_{\rm gas-dust}$\,=\,BLAH, consistent with Combes+13: 206 ?
 Typical local (U)LIRGs are found to have a
gas-to-dust mass ratio of 200$-$350 (Sanders et al. 1991; Contini
\& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).

>>>>

\subsection{SED modeling} \label{sec:SED}  % DONE
We fit dust SED models to the
24\,\micron$-$2.2\,mm photometry in \Fig{SED}, where we also
include the IRAS 60\,$\micron$ and 100\,$\micron$ upper limits
to constrain the dust peak.
The fit is performed with the code
\ncode{mbb\_emcee} \citep[\eg][]{Dowell14a}, which samples the posterior
using an MCMC approach and uses instrumental
response curves to perform color correction on-the-fly.
The SED model consists of a modified-blackbody
function with a power-law attached to the
Wien side to account for an excess in the MIR owing to warm,
small dust emission.
% Previous studies find that in the absence of mid-IR data, a powerlaw slope
% of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, % for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
%
%We add $\sim$15\% calibration uncertainties in quadrature to obtain the total
%uncertainties for the PdBI continuum in our fitting procedure.
The model is thus described by five free parameters: the rest-frame characteristic dust
temperature (T$_{d}$), the emissivity index ($\beta$), the power-law index
($\alpha$), the flux normalization at 500\,$\micron$ ($f_{\rm norm}$), and
the observed-frame wavelength at which the emission
becomes optically thick ($\lambda_{0}$). We impose
an upper limit of 100\,K on $T_d$, a Gaussian prior centered around
$\mu$\,=\,1.9 with $\sigma$\,=\,0.3 on $\beta$, and an upper limit of
1000$\micron$ on $\lambda_0$.
We check for chain convergence by requiring the autocorrelation
length of each parameter to be less than the number of steps
taken for the burn-in phase (which are then discarded).
Here we report the modes %in log file
% summary statistics (global mode (where min. chi),
% marginal mode (in log file), posterior median (instead of posterior means;
% need to compute)
and the 1$\sigma$ confidence intervals in the marginal PDFs
as the best-fit parameters, as listed in \Tab{SED}.

@@

In the first model, we include the 24\,$\micron$ data
to constrain the power-law index. Based on the
best-fit of this model, we find a
\fir luminosity (rest-frame 42.5$-$122.5\,$\micron$) of
3.81\petm{2.04}{1.92}\E{12}\,\Lsun and a
dust mass of 22\petm{5}{18}\E{8}\,\Msun.
For the mass absorption coefficient, we adopt
$\kappa$\,=\,2.64\,m$^2$kg\pmOne at 125.0\,$\micron$
(rest frame; \citealt{Dunne03a}).
The dust mass uncertainty does not
include those in the absorption coefficient.
These values are not corrected for lensing.

A fit including the MIR 24\,$\micron$ photometry
is likely an upper limit on the \fir luminosity arising from starburst.
% since the fit include contribution from the AGN (through power-law to MIR)
If we instead fit for a model excluding the 24\,$\micron$ constraint,
two major consequences are immediately apparent.
First, the power-law index is poorly-constrained (see \Tab{SED}).
Second, the steep power-law implies a small contribution
from the power-law regime
to the total IR luminosity as compared to the graybody.
Thus, the \fir luminosity in
this model should, in principle, corresponds to a
lower limit on the cold dust emission.
Using the best-fit parameters
for this model, we find a  \LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun.
Again, the inferred quantities are uncorrected for lensing.
%The best-fit SEDs are shown in \Fig{SED} and the
% resulting parameters are listed in \Tab{SED}.

The dust temperature from both models is similar to that of
ULIRGs at 0.6\,$<$\,$z$\,$<$\,1.0 (54\,$\pm$\,5\,K; \citealt[hereafter C13]{Combes13a}).
We note the \fir luminosities from both models are comparable, which is
not surprising given the lack of constraints in the MIR. In fact, the
\fir luminosity from the second model is slightly higher than the former, but
consistent within the uncertainties.
For the subsequent analysis, we adopt the physical quantities
from the former model. The choice of which fit does not affect
the derived star formation rate (SFR) given the similar \fir luminosity.
Yet, the dust mass is higher in the former (but consistent within the
uncertainties), and thus the gas-to-dust ratio in \Sec{properties}
should be considered as an estimate.

@@

We correct for lensing using the median magnification factor $(\mu_{\rm L}\eq5.5)$
from the CO lens models. This yields a \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun.
Assuming a Salpeter initial
mass function \citep{Salpeter55a}, we find a
SFR of (120\pmm63)\,\Msun\,yr\pmOne using the
standard conversion \citep{Kennicutt98a}. 
In the following section, we compare the properties of RXJ1131 
with those reported by C13, which is the largest sample of
ULIRGs at similar redshift (0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements,
to place RXJ1131 in context of existing studies.  
Since C13 adopt a different definition of 
\LFIR (40$-$500\micron)\footnote{We also note that the \fir luminosity in C13 is derived 
based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.}, we derive the \fir luminosity
following this convention.
This yields \LFIR of $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)$\,\Lsun and 
a SFR of $($150\pmm 70$)$\,\sfrU. 
This implies RXJ1131 is considered a LIRG in regards to their sample, and consequently, 
the SFR of RXJ1131 is lower than the C13 sample (SFR $>$ 200, with an average of 1200).

\subsection{Gas properties} \label{sec:properties}
In this section, we derive the gas properties of RXJ1131 based on \bco,
and compare the derived quantities against those reported by
C13, where their results are based on \bco and \rot{4}{3} line observations on the IRAM 30-m dish.

@@

Without direct \rot{1}{0} measurements,
we derive \rot{1}{0} intensity
using a brightness temperature ratio of $r_{\rm 32}$\,=\,1, which was chosen
solely to facilitate a comparison with the C13 sample. For the same reason, we
adopt a luminosity-to-mass conversion factor of
\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne. This yields
\Lp\,=\,(3.47\,$\pm$\,1.58)\E{10}\,\Lsun and a gas mass
of (2.8$\pm$1.3)\,\E{10} \Msun. This is likely
an overestimation due to a contribution from the companion, but 
comparable to the C13 sample ($M_{\rm gas}$\,=\,1.5\E{10}\Msun) within the
uncertainties.

% gas-to-dyn ratio
Using the dynamical mass of BLAH (see \Sec{dynamics}), we find
a gas-to-dynamical mass fraction of $f_{\rm gas-dyn}$\,=\,BLAH.
% gas to dust ratio:
Based on the dust mass derived from SED fitting, we find a gas-to-dust ratio of
$f_{\rm gas-dust}$\,=\,70\petm{blah}{blah}, consistent with Combes+13: 206 ?
% Typical local (U)LIRGs are found to have a
%gas-to-dust mass ratio of 200$-$350 (Sanders et al. 1991; Contini
%\& Contini 2003; Seaquist et al. 2004; Wilson et al. 2008).

### 2016-05-25 WRITEUP/table_magFactor.tex
add table note
typeset edits
done dyn modelling
fix typo
SED section close to done
updated SED section with SFR and comparison to C13 sameple, but LIR and FIR/IR fraction, etc

\begin{deluxetable}{lccc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{\rot{2}{1} Magnification factors.}
\tablehead{
\colhead{channel} & 
\colhead{Source 1 $\mu_{\rm L}$} & 
\colhead{Source 2 $\mu_{\rm L}$} & 
}
\startdata
126-130 & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\ %which is source 1 and 2 then?
131-135 & 7.6 $\pm$ 1.6 & \\ % would this be source 1 or 2?
136-140 & 8.7 $\pm$ 2.0 & \\
141-145 & 4.1 $\pm$ 0.9 & \\
146-150 & 4.2 $\pm$ 0.6 & \\
151-156 & 4.3 $\pm$ 2.4 & \\
156-160 & 3.1 $\pm$ 0.9 & \\
weighted average & 4.4 & \\
median & 5.5 &  \\
\enddata
\label{tab:mag}
\tablecomments{blah}
 %TablenotegoesBetween 
\tablerefs{blah}
\end{deluxetable}

>>>>

\begin{deluxetable}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Magnification factors of various kinematic components in \bco}
\tablehead{
\colhead{Channel} &
\colhead{Source 1 $\mu_{\rm L}$} &
\colhead{Source 2 $\mu_{\rm L}$}
}
\startdata
126$-$130 & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\ [0.6ex] %which is source 1 and 2 then?
131$-$135 & 7.6 $\pm$ 1.6 & \\ [0.6ex] % would this be source 1 or 2?
136$-$140 & 8.7 $\pm$ 2.0 & \\ [0.6ex]
141$-$145 & 4.1 $\pm$ 0.9 & \\ [0.6ex]
146$-$150 & 4.2 $\pm$ 0.6 & \\ [0.6ex]
151$-$155 & 4.3 $\pm$ 2.4 & \\ [0.6ex]
156$-$160 & 3.1 $\pm$ 0.9 & \\ [0.6ex]
weighted average & 4.4 & \\ [0.6ex]
median & 5.5 &
\enddata
\label{tab:model}
\tablecomments{Source 1 is RXJ1131 and source 2 is its companion. See text for details.}
\end{deluxetable}
